### 2020-04-03 06-examples.tex
vari cambi file sforamenti linea
cambi in file con sforamento linea

Here, the entities $T$ and $T'$ that can be produced by the reactions and that are not provided by the context:
\[
\begin{array}{lcllcl}
P (T,\widetilde{T})&\defeq & \sum_{h=0}^1 (\startchain{T_i}\chainedlink{T_o}{\noact}\chainend{\noact})^h\ \link{\widetilde{T}_i}{\widetilde{T}_o}.P (T,\widetilde{T})
& +  && \link{T_i}{T_o}.P (\overline{T},\widetilde{T}) \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl}
P_T & \defeq & P(T,\widetilde{T})& \overline{P}_T & \defeq & P(\overline{T},\widetilde{T}) & P_{T'}& \defeq & P(T',\widetilde{T'}) & \overline{P}_{T',\widetilde{T'}}& \defeq & P(\overline{T'},\widetilde{T'})\\\
\end{array}
\]
Here, the entities that can be produced by the reactions and that can be  provided by the context:
\[
\begin{array}{lcl @{\hspace{1cm}}lcl}
P(C,\widehat{C},\underline{C},\widetilde{C}) & \defeq &  \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\widehat{C}_i}{\widehat{C}_o} (\startchain{\noact}\chainedlink{\noact}{\widetilde{C}_i}\chainend{\widetilde{C}_o})^h.   P(C,\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
&& \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o}.P(\overline{C},\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
 && \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o} \startchain{\noact}\chainedlink{\noact}{\widehat{C}_i}\chainend{\widehat{C}_o}.   P(C,\widehat{C},\underline{C},\widetilde{C}) \\
 %&  \overline{E} (a)&\defeq & \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{a}_i}{\widehat{a}_o}.E(a)\\
%&&  &  && +\\
%&& 
%&
%&& \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\underline{a}_i}{\underline{a}_o}.\overline{E}(q)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{1cm}}lcl@{\hspace{0.4cm}}lcl@{\hspace{0.4cm}}lcl}
P_C & \defeq &  P(C,\widehat{C},\underline{C},\widetilde{C})&  P_G& \defeq &   P(G,\widehat{G},\underline{G},\widetilde{G}) \\
\overline{P}_C & \defeq &  P(\overline{C},\widehat{C},\underline{C},\widetilde{C}) & 
\overline{P}_G& \defeq &   P(\overline{G},\widehat{G},\underline{G},\widetilde{G})\\
\end{array}
\]

>>>>

Here, the entities $T$ and $T'$ that can be produced by the reactions and that are not provided by the context:
\[
\begin{array}{lcllcl}
P (T,\widetilde{T})&\defeq & \sum_{h=0}^1 (\startchain{T_i}\chainedlink{T_o}{\noact}\chainend{\noact})^h\ \link{\widetilde{T}_i}{\widetilde{T}_o}.P (T,\widetilde{T})
& +  && \link{T_i}{T_o}.P (\overline{T},\widetilde{T}) \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl}
P_T & \defeq & P(T,\widetilde{T})& \overline{P}_T & \defeq & P(\overline{T},\widetilde{T}) & P_{T'}& \defeq & P(T',\widetilde{T'}) & \\
\overline{P}_{T',\widetilde{T'}}& \defeq & P(\overline{T'},\widetilde{T'})\\\
\end{array}
\]
Here, the entities that can be produced by the reactions and that can be  provided by the context:
\[
\begin{array}{lcl @{\hspace{1cm}}lcl}
P(C,\widehat{C},\underline{C},\widetilde{C}) & \defeq &  \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\widehat{C}_i}{\widehat{C}_o} (\startchain{\noact}\chainedlink{\noact}{\widetilde{C}_i}\chainend{\widetilde{C}_o})^h.   P(C,\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
&& \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o}.P(\overline{C},\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
 && \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o} \startchain{\noact}\chainedlink{\noact}{\widehat{C}_i}\chainend{\widehat{C}_o}.   P(C,\widehat{C},\underline{C},\widetilde{C}) \\
 %&  \overline{E} (a)&\defeq & \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{a}_i}{\widehat{a}_o}.E(a)\\
%&&  &  && +\\
%&& 
%&
%&& \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\underline{a}_i}{\underline{a}_o}.\overline{E}(q)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{1cm}}lcl@{\hspace{0.4cm}}lcl@{\hspace{0.4cm}}lcl}
P_C & \defeq &  P(C,\widehat{C},\underline{C},\widetilde{C})&  P_G& \defeq &   P(G,\widehat{G},\underline{G},\widetilde{G}) \\
\overline{P}_C & \defeq &  P(\overline{C},\widehat{C},\underline{C},\widetilde{C}) & 
\overline{P}_G& \defeq &   P(\overline{G},\widehat{G},\underline{G},\widetilde{G})\\
\end{array}
\]
